Extended Data

### 2022-03-13 doc/manuscript/Dow_manuscript_Nature.Rmd
comment out sample sizes
@camerondow35 , was this change specifically requested by reviewers? It really breaks up the sentence/ makes it difficult to read. I instead added a citation of the table with this info. If we need to present these numbers in the text, I'd find a different way to do it, but I don't see why citing the table wouldn't be sufficient.

Using dendrometer band measurements taken throughout multiple growing seasons at the Smithsonian Conservation Biology Institute (SCBI; Virginia, USA; n = `r n_dendro_trees_SCBI` trees from 2011-2020) and Harvard Forest (Massachusetts, USA; n = `r n_dendro_trees_HF` trees from 1998-2003), we fit a logistic growth model[@mcmahon_general_2015] to determine the days of year (DOY) when 25, 50, and 75% annual growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$), peak growing season length ($L_{pgs}= DOY_{75}$-$DOY_{25}$), the maximum daily growth rates ($g_{max}$; occurs on average within 5 days of $DOY_{50}$), and total annual increment in diameter at breast height ($\Delta DBH$; Fig. `r schematic_summary`). 
This analysis was performed separately for ring- (67 trees at SCBI and 138 trees at Harvard Forest) and diffuse porous (52 trees at SCBI and 183 trees at Harvard Forest) species, which differ in the seasonal timing of growth[@dorangeville_peak_2021;@tumajer_limitation_2022]. 
These stem-growth milestones were compared to canopy foliage phenology (measured at ecosystem level via remote sensing).

>>>>

Using dendrometer band measurements taken throughout multiple growing seasons at the Smithsonian Conservation Biology Institute (SCBI; Virginia, USA; n = `r n_dendro_trees_SCBI` trees from 2011-2020) and Harvard Forest (Massachusetts, USA; n = `r n_dendro_trees_HF` trees from 1998-2003), we fit a logistic growth model[@mcmahon_general_2015] to determine the days of year (DOY) when 25, 50, and 75% annual growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$), peak growing season length ($L_{pgs}= DOY_{75}$-$DOY_{25}$), the maximum daily growth rates ($g_{max}$; occurs on average within 5 days of $DOY_{50}$), and total annual increment in diameter at breast height ($\Delta DBH$; Fig. `r schematic_summary`). 
This analysis was performed separately for ring- <!--(67 trees at SCBI and 138 trees at Harvard Forest)-->and diffuse porous <!--(52 trees at SCBI and 183 trees at Harvard Forest)-->species (`r EDT_species`), which differ in the seasonal timing of growth[@dorangeville_peak_2021;@tumajer_limitation_2022]. 
These stem-growth milestones were compared to canopy foliage phenology (measured at ecosystem level via remote sensing).
